\input{../styles/handout-leader}
\def\mytitle{Aggregation}
\def\myauthor{Assignment 7}
\def\mydate{Due March 23, 5pm}
\input{../styles/handout-begin}

\noindent Answer \textbf{one} of the two following questions, in about 400-500 words. You should answer the question at the end, defend your answer, and say a bit about the best argument for the opposing answer, and why you don't think that argument works.

\section*{Question One}

Alice, Betty and Carla are deciding where to go for brunch. They have two choices, the Diner or the Eatery. They have talked about each of the following propositions, and have settled views about each of them.

\begin{itemize}
\item P1 - Does the Diner serve only free range eggs?
\item P2 - Does the Eatery serve only free range eggs?
\item P3 - Which place has tastier food?
\item P4 - Should we boycott restaurants that serve eggs that are not free range?
\item P5 - Should we go to the restaurant with the tastiest food that we are not boycotting?
\item P6 - Where should we eat?
\end{itemize}
Here are their views on these questions.

\begin{center}
\begin{tabular}{r c c c c c c}
 & \textbf{P1} & \textbf{P2} & \textbf{P3} & \textbf{P4} & \textbf{P5} & \textbf{P6} \\
\textbf{Alice} & Yes & Yes & Eatery & Yes & Yes & Eatery \\
\textbf{Betty} & Yes & No & Eatery & Yes & Yes & Diner \\
\textbf{Carla} & Yes & No & Eatery & No & Yes & Eatery
\end{tabular}
\end{center}
Where should the friends eat?

\section*{Question Two}

Alice is offered a choice of two bets that concern a pair of basketball games. The Ducks are playing in the first game, and the Emus are playing in the second game.

\begin{itemize}
\item Option A wins \$100 if the Ducks and Emus both win, and nothing otherwise.
\item Option B wins \$50 if either the Ducks or the Emus lose (i.e., if it is not the case that Option A wins), and nothing otherwise.
\end{itemize}
Alice must chose one, and just one, of these options.

Alice knows almost nothing about basketball, so she asks her two friends Betty and Carla. They both have lots of knowledge about basketball, and have extremely good track records at forecasting basketball games.

Betty says that the two games are probabilistically independent, and each team (the Ducks and the Emus) has an 80\% chance to win their game. So the chance that Option A will win is 64\%, and the chance that Option B will win is 36\%.

Carla says that the two games are probabilistically independent, and each team (the Ducks and the Emus) has an 30\% chance to win their game. So the chance that Option A will win is 9\%, and the chance that Option B will win is 91\%.

Alice has no other information about the games. Which option should she take?


\end{document}