---
title: "444 Lecture 2.5 - Famous Games"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

- Set out some famous games

## Associated Reading

No particular reading; these are scattered through the book.

## Prisoners' Dilemma

```{r}
game <- tribble(
  ~Moves,       ~Coop, ~Defect,
  "Coop",      "3, 3", "0, 5",
  "Defect",    "5, 0", "1, 1"
)
gameformat(game)
```

## Generic Symmetric Game

```{r}
game <- tribble(
  ~Moves,       ~X, ~Y,
  "X",    "a, a", "b, c",
  "Y",    "c, b", "d, d"
)
gameformat(game)
```

## Prisoners' Dilemma

```{r}
game <- tribble(
  ~Moves,       ~X, ~Y,
  "X",    "a, a", "b, c",
  "Y",    "c, b", "d, d"
)
gameformat(game)
```

Ordinal constraints

- $c > a, d > b$
- $a > d$

Cardinal constraints

- $2a > b + c$

## Stag Hunt

```{r}
game <- tribble(
  ~Moves,       ~Coop, ~Defect,
  "Coop",      "5, 5", "0, 4",
  "Defect",    "4, 0", "2, 2"
)
gameformat(game)
```

## Stag Hunt

```{r}
game <- tribble(
  ~Moves,       ~X, ~Y,
  "X",    "a, a", "b, c",
  "Y",    "c, b", "d, d"
)
gameformat(game)
```

Ordinal constraints

- $a > c, d > b$
- $a > d$

Cardinal constraints

- $a + b < c + d$

## Battle of the Sexes

```{r}
game <- tribble(
  ~Moves,       ~Row, ~Col,
  "Row",    "4, 1", "0, 0",
  "Col",    "0, 0", "1, 4"
)
gameformat(game)
```

## Battle of the Sexes (relabelled)

```{r}
game <- tribble(
  ~Moves,       ~Self, ~Other,
  "Self",    "0, 0", "4, 1",
  "Other",    "1, 4", "0, 0"
)
gameformat(game)
```

## Chicken

```{r}
game <- tribble(
  ~Moves,       ~Attack, ~Retreat,
  "Attack",    "-99, -99", "2, 0",
  "Retreat",    "0, 2", "1, 1"
)
gameformat(game)
```

## Rock Paper Scissors

```{r}
game <- tribble(
  ~Moves,        ~Rock,   ~Paper, ~Scissors,
  "Rock",       "0, 0",  "-1, 1", "1, -1",
  "Paper",     "1, -1",   "0, 0", "-1, 1",
  "Scissors",  "-1, 1",  "1, -1", "0, 0"
  )
gameformat(game)
```

## For Next Time

We're jumping ahead to section 2.5 of Bonanno.
