---
title: "444 Lecture 2.7 - Iterated Deletion of Weakly Dominated Strategies"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

To look at two problems that arise when we delete strategies that are merely weakly dominated.

## Reading

Bonanno, section 2.5.2.

## Two Issues

- Order effects.
- Philosophical motivation.

## Order Effects

- As Bonanno goes over, when deleting weakly dominated strategies, it matters what order you do the deletions in.
- Whether a strategy weakly dominates another at a point in the process might depend on how you got to that point.
- And the result is that different ways of applying the process lead to different 'solutions'.

## Way Around This

- Bonanno says (as I think is standard) that you solve this by saying that at each stage, you delete every strategy that you possibly can.
- There is still an issue I think about why that deletion process is justified as opposed to some other.
- It does have the nice advantage of actually being a well defined process, so that's nice.

## Philosophical Justification

- The bigger issue is that it is a little hard to say why we should care about the result of this procedure.
- Saying what's special about the result of this strategy is not completely obvious.
- Bonanno alludes to this - let's go over it in a bit more detail.

## Iterated Deletion

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "1, 1",  "1, 1", "0, 0",
  "Middle", "1, 1",  "0, 0", "1, 0",
  "Down",   "0, 0",  "0, 1", "1, 1"
)
gameformat(game)
```

- Middle weakly dominates Down, and Center weakly dominates Right.
- So let's delete them.

## Iterated Deletion

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, 
  "Up",     "1, 1",  "1, 1", 
  "Middle", "1, 1",  "0, 0"
)
gameformat(game)
```

- Now Up weakly dominates Middle and Left weakly dominates Center.
- So the solution is Up/Left, right?
- Well, not so fast.

## Iterated Deletion

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "1, 1",  "1, 1", "0, 0",
  "Middle", "1, 1",  "0, 0", "1, 0",
  "Down",   "0, 0",  "0, 1", "1, 1"
)
gameformat(game)
```

- Think about it from Row's perspective.
- We have an argument that Column will play Left.
- If that argument works, Row shouldn't prefer Up - they should be indifferent between Up and Middle.
- Why does the argument say to play Up then?

## Iterated Deletion

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "1, 1",  "1, 1", "0, 0",
  "Middle", "1, 1",  "0, 0", "1, 0",
  "Down",   "0, 0",  "0, 1", "1, 1"
)
gameformat(game)
```

- The answer is that Middle is risky.
- In the game after deletion, Middle has a risk of getting 0, but Up is sure to get 1.

> - But look at the original game - Up is risky too!
> - I think this makes it hard to philosophically defend IDWDS

## For Next Time

We will look at a famous example of iterated deletion that's not in the book.

