---
title: "444 Lecture 5.1 - Cardinal Games"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

Talk about why we might care about having cardinal payouts in games.

## Reading

Bonanno, section 6.1

## Games with Lotteries

Here is one thing we can do with cardinal utilities - include lotteries in the payoffs.

- We can treat the lottery ticket as having a value equal to the **expected value** of the lottery.

## Games with Lotteries

Bonanno illustrates this with a game that involves an actual lottery - an auction where tied bids are resolved by a chance mechanism.

- But philosophically, lots of things in life look like lottery ticket.
- How much is $1  million worth? \pause
- It depends a bit on whether there is lots of inflation in the near future. \pause
- It also depends on whether there is a revolution soon and millionaires are in danger.

## Everything's a Gamble

The orthodox treatment of these questions, which I totally endorse, is that a quantity of money is just as much a gamble as a lottery ticket.

- It's a relatively safe gamble; there hasn't been hyperinflation or anti-capitialist revolution in America in a long time.
- But it's a gamble.
- So even games with monetary payouts are gambles - gambles on the future value of money.

## Chicken 1

Here is a version of chicken using ordinal utility.

```{r}
game <- tribble(
  ~Moves,         ~swerve, ~drive,
  "Swerve",  "3, 3", "2, 4",
  "Drive",  "4, 2", "1, 1"
)
gameformat(game)
```

## Chicken 2

```{r}
game <- tribble(
  ~Moves,         ~swerve, ~drive,
  "Swerve",  "1, 1", "0, 2",
  "Drive",  "2, 0", "-5, -5"
)
gameformat(game)
```

I guess you mostly swerve in this game, but you think about driving.

## Chicken 3

```{r}
game <- tribble(
  ~Moves,         ~swerve, ~drive,
  "Swerve",  "1, 1", "0, 2",
  "Drive",  "2, 0", "-5000, -5000"
)
gameformat(game)
```

Please swerve! \pause

- But (Swerve, swerve) is not Nash. We'll come back to this.

## Cardinal Utility Matters

- The last two games were alike in ordinal utility.
- But they were unlike in how you should play them.
- So more than ordinal utility matters for how you should play.

## For Next Time

We will introduce an important means for solving games like Chicken - the mixed strategy.