---
title: "444 Lecture 5.3 - Mixed Strategies in Equilibria"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

Discuss the existence of mixed strategy equilibria.

## Reading

Bonanno, section 6.2

## Key Theorem

In any finite game in which all mixtures of strategies are available, there is at least one Nash equilibria.

## Example

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "2, 0", "0, 3", 
  "Down",  "0, 1", "1, 0"
)
gameformat(game)
```

Let's discuss this game for a bit. Does it have an equilibrium?

## Example

```{r}
gamebox <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "\\fbox{2}, 0", "0, \\fbox{3}", 
  "Down",  "0, \\fbox{1}", "\\fbox{1}, 0"
)
gameformat(gamebox)
```

No Nash equilibrium in pure strategies.

## A Strategy for Row

```{r}
gameformat(game)
```

Consider what happens if Row plays

- Up with probability $\nicefrac{1}{4}$;
- Down with probability $\nicefrac{3}{4}$.

## Column's Expected Return

```{r}
gameformat(game)
```

Column's expected return from playing Left is 

- 0 with probability $\nicefrac{1}{4}$ plus
- 1 with probability $\nicefrac{3}{4}$, i.e.,
- $\nicefrac{3}{4}$.

## Column's Expected Return

```{r}
gameformat(game)
```

Column's expected return from playing Right is 

- 3 with probability $\nicefrac{1}{4}$ plus
- 0 with probability $\nicefrac{3}{4}$, i.e.,
- $\nicefrac{3}{4}$.

## Column's Expected Return

```{r}
gameformat(game)
```

- So either way, Column's expected return from playing a pure strategy is $\nicefrac{3}{4}$.
- And hence Column's expected return from playing any mixture of the two pure strategies is $\nicefrac{3}{4}$.

## A Strategy for Column

```{r}
gameformat(game)
```

Consider what happens if Column plays

- Left with probability $\nicefrac{1}{3}$;
- Right with probability $\nicefrac{2}{3}$.

## Row's Expected Return

```{r}
gameformat(game)
```

Row's expected return from playing Up is 

- 2 with probability $\nicefrac{1}{3}$ plus
- 0 with probability $\nicefrac{2}{3}$, i.e.,
- $\nicefrac{2}{3}$.

## Column's Expected Return

```{r}
gameformat(game)
```

Row's expected return from playing Down is 

- 0 with probability $\nicefrac{1}{3}$ plus
- 1 with probability $\nicefrac{2}{3}$, i.e.,
- $\nicefrac{2}{3}$.

## Column's Expected Return

```{r}
gameformat(game)
```

- So either way, Row's expected return from playing a pure strategy is $\nicefrac{2}{3}$.
- And hence Row's expected return from playing any mixture of the two pure strategies is $\nicefrac{2}{3}$.

## An Equilibria

```{r}
gameformat(game)
```

- What happens if they both play the mixed strategies we've been discussing? \pause
- It's an equilibria.

## An Equilibria

```{r}
gameformat(game)
```

- Whatever Column does, their expected return is $\nicefrac{3}{4}$.
- So they can't do better than play this mixed strategy.
- They can't do worse either, but the definition of equilibrium just requires that they can't do better.

## An Equilibria

```{r}
gameformat(game)
```

- Whatever Row does, their expected return is $\nicefrac{2}{3}$.
- So they can't do better than play this mixed strategy.
- They can't do worse either, but the definition of equilibrium just requires that they can't do better.

## Two General Points

> 1. There is always some equilibria like this (at least in finite games), even if it doesn't look like it at first.
> 2. Typically, the way we find equilibria is making the other player indifferent between a bunch of options.

## For Next Time

We will use that last point to work out how to compute the Nash equilibria for simple games.