\input{../styles/handout-leader}
\def\mytitle{Feb 15}
\def\myauthor{Brian Weatherson}
\def\mydate{February 15, 2018}
\input{../styles/handout-begin}

\section{Start with probabilities}
\label{startwithprobabilities}

Update by conditionalisation

\section{Do we do AGM? Probably not.}
\label{dowedoagmprobablynot.}

\begin{itemize}
\item{} But two big puzzles

\item{} One is update on `impossible' evidence

\item{} Other is contraction

\item{} Arguably one solution will work for both

\item{} Impossible update = contraction plus update

\item{} That's contentious - not obviously a definition - but plausble

\end{itemize}

\section{Like-mindedness}
\label{like-mindedness}

\begin{itemize}
\item{} Common prior

\item{} That's what we end up with

\end{itemize}

\section{What Aumann's theory states}
\label{whataumannstheorystates}

\begin{itemize}
\item{} If there is a common prior, and it is common knowledge what the posteriors are, the posteriors must be equal.

\end{itemize}

\section{Other versions of Aumann}
\label{otherversionsofaumann}

\begin{itemize}
\item{} Can't have common knowledge of expectation

\item{} Can't have common knowledge of which side of expectation

\item{} Can have common knowledge of non-agreement on expectation (including probability)

\item{} Can't have common knowledge of average of probabilities!

\item{} Can't have common knowledge of action, given common action plan and common prior - but this is tricky, and requires some strong assumptions about plans - in particular requires a strong version of Sure Thing Principle

\item{} No trade theorems (though these are a bit boring)

\end{itemize}

\section{Need common prior}
\label{needcommonprior}

\begin{itemize}
\item{} Trivial to get counterexamples without it

\item{} Just have no information, and distinct priors and done

\item{} I mean, it's a bit tougher than that, but that's roughly the idea

\end{itemize}

\section{What about with just S4}
\label{whataboutwithjusts4}

\begin{itemize}
\item{} That's trickier, because don't often have perfect knowledge of own probability!

\item{} But what if you do?

\item{} I don't know. Sob. Sob.

\end{itemize}

\end{document}
