---
title: "444 Lecture 9"
subtitle: "Mixed Strategies and Philosophy"
date: "February 7, 2023"
---


```{r, include=FALSE}
source("kableformat.R")
```

# Dominance by Mixture

## Basic Example

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 0", 
  "Middle", "1, 0", "1, 0",
  "Down",  "0, 0", "3, 0"
)
gameformat(game)
```

This is a bit boring for Column, but let's focus on Row for now.

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}

At first it looks like there are no dominated strategies.
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
- Up does worse than Middle and Down if Column plays Right, so it doesn't dominate anything.
- Middle does worse that Up if Column plays Left, and worse than Down if Column plays Right.
- Down does worse than both of them if Column plays Left.
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}

But compare these two strategies.

:::::{.nonincremental}
- Middle
- The mixed strategy of Up with probability 0.5, and Down with probability 0.5.
:::::

::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
- Middle gets an actual return of 1 whatever Column does.
- The mixed strategy gets an expected return of 1.5 whatever Column does.
- So it has a higher expected return given Left (1.5 > 1), and a higher expected return given Right (1.5 > 1).
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
- If that happens, then we'll say that Middle is dominated by this mixture.
- When we're deleting dominated strategies, we should delete it too.
::::

:::

## Nash and Dominance

- A strategy that is dominated by a mixture like this can never be part of a Nash equilibrium.
- After all, the player would be better off playing the mixture than playing it, so it fails the test that there is nothing better to do.
- So being able to find these dominating mixtures can be very helpful in working out what the Nash equilibrium is.

## Rational Play and Dominance

- But even beyond that, it seems wrong to play strategies that are dominated in this way.
- If you're thinking about playing Middle (as Row), you increase your expected return by simply flipping a coin to choose between Left and Right.
- So that's what you should do.

# Best Responses

## {.plain}

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 0",
  "Middle", "2, 0", "2, 0",
  "Down",  "0, 0", "3, 0"
)
```


::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}

-   Up is the best response to Left.
-   Down is the best response to Right.
-   Is Middle the best response to anything?

::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
Yes!

-   Middle is the best response to the mixed strategy Left with probability 0.5, Right with probability 0.5.
-   It gets 2, the other options have an expected return of 1.5.
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}

-   Middle is the best thing to do if you know Column is going to flip a coin to decide what to do.
-   But it's also the best thing to do if you have no idea what Column is going to do, and the best you can do is say it's 50/50 what they are going to do.
-   So it's actually pretty easy to think of situations where Middle is the smart play.
::::

:::

## Best Response

-   A strategy $S$ is a **best response** just in case...
-   There is some probability distribution over the other player's strategies and ...
-   No strategy has a higher expected return than $S$ given that probability distribution.

## Best Response

-   Note that this allows for ties.
-   Weakly dominated strategies can even be best responses in this sense. \pause
-   This definition also covers mixed strategies; they can also be best responses.

## A Surprising Theorem

-   Say a strategy is **undominated** if no other strategy, pure or mixed, strongly dominates it.
-   And it is a **best response** if it does as well as anything, given at least one probability distribution.
-   Here's the surprising theorem:

\pause
> The strategies that are best responses are just the same strategies as those that are undominated.

## Best Reponses

-   This relates back to something I was saying in the last lecture.
-   The strategies that are dominated by mixtures didn't seem to make sense - you could just play the mixtures.
-   But here's another property that they have - they are never best responses.

## Best Reponses

-   And if they are not best responses, no one can play them while maximising expected utility.
-   Whatever probability you give to the other player's play, if you maximise expected utility you will play a best response.
-   And you should maximise expected utility.

# Rationalizable Strategies


```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 1",
  "Middle", "1, 1", "1, 0",
  "Down",  "0, 0", "3, 1"
)
```

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}

In this game, the best responses are:

- Row can play Up (best response to Left) or Down (best response to Right);
- Column can play Left (best response to Middle) or Right (best response to either Up or Down).
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
- But Middle is not a best response.
- It is dominated by the 50/50 mixture of Left and Right.
::::

:::

## {.plain}

::: {.columns}

:::: {.column width="40%"}

```{r}
gameformat(game)
```

::::

:::: {.column width="60%"}
- So while Left is a best response...
- It is not a best response to a best response.
::::

:::

## Iterated Best Responses

- That makes it seem irrational to play Middle.
- I could build more complicated examples, where we had cases that are best responses to best responses, but not best responses to best responses to best responses.

## Iterated Best Responses

- Actually we've already seen such a case.
- In the Ice Cream game, 2 is a best response to 1, which is a best response to 0.
- But 2 is not a best response to any best response to a best response.

## Iterated Best Responses

- Some strategies are at the start of an infinite chain $S_1, S_2, \dots$ where each strategy is a best response to the one that comes after it.
- Call these the **rationalizable** strategies.

## Infinite Chains

Here is one way to get an infinite chain like this.

- If the pair $\langle S_1, S_2 \rangle$ is a Nash equilibrium, ...
- Then $S_1$ is a best response to $S_2$, which is a best response to $S_1$, which is a best response to $S_2$, which ... \pause
- But you don't only need to use Nash equilibria.

## Infinite Chains

- Think about Rock, Paper, Scissors.
- Rock is a best response to Scissors, which is a best response to Paper, which is a best response to Rock, which is...
- But Rock is not part of a Nash equilibrium.

## Rationalizability

I'm not going to prove this, but the following turns out to be true.

- The strategies that can be at the start of these infinite chains ...
- Are exactly those strategies that survive iterated deletion of strongly dominated strategies ...
- Provided we include dominance by mixtures when we're doing the deleting.

## Philosophical Payoff

Some economists, and a few philosophers, have argued that this is the key philosophical notion in game theory.

- They say that a strategy is rational to play if and only if it is rationalizable in this sense.
- In economics, this is very much a **heterodox** view.
- Note that this view is more permissive than the view that rational players will choose Nash equilibria.

## Philosophical Payoff

- All Nash equilibria are rationalizable, but some rationalizable strategies (e.g., Rock!), are not Nash equilibria.
- Most economists think that if there is a key notion in game theory, it is **less permissive** than Nash equilibrium.

# Why Nash?

## Reading

Bonanno, sections 2.6 (which we discussed earlier) and 6.4.

## Two Conjectures

1. It is rational to play any rationalizable strategy.
2. It is only rational to play Nash Equilibrium strategies

I'm going to end this week talking a bit about why people might prefer 2 over 1.

## One Intuitive Idea

- Don't just play Rock - the other person will figure it out.
- Rock every time is rationalizable.
- But you shouldn't do it.
- Therefore principle 1 must be false.

## Response 1

- Yeah, you shouldn't play Rock every single time, that's dumb.
- But on any given occasion, it's fine.
- And we know, from e.g., Prisoners' Dilemma, that we shouldn't infer what to do in a single shot game from what happens in the repeated game.

## Response 2

- The orthodox solution (i.e., principle 2) actually doesn't give you the result you might want here.
- It is possible that the randomising device will come up Rock every single time.
- So if you think it's always irrational to play Rock repeatedly, you have to think both of these are wrong.

## Response 3

- If principle 2 is right, all rational players will randomise every time.
- So the expected return of Rock is just the same as the expected return of randomisation.
- So it can't be wrong to play it.

## Mixing Response 2 and Response 3

- If principle 2 is right, and it's common knowledge that the players are rational, then the rational way to interpret the other player playing Rock every time is "Wow, their random device is having a freaky run."
- But if that's right, there isn't anything wrong with playing Rock every time.

## Other Direction

- As we'll see when we get to O'Connor's book, you mostly see people wanting more restrictions on moves than Nash.
- But Bonanno ends chapter 6 with an interesting reason for thinking even rationalisability (i.e., IDSDS) is too strong.

## Other Direction

- It's really incredibly unrealistic to know the utility function that the other player has.
- You might know the physical outcomes of the game, but knowing what utility each player gets is a huge assumption.
- So in practice, you should probably not rely too heavily on theories or policies that rely on this knowledge.

## For Next Time

- Next week we will do a bit of revision of probability theory.
- It's completely optional, and will be very familiar to many people here; if you want a day off, take a day off.
- After that, we'll look at how game theorists think about signals and messages.

