% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[BoldFont = SF Pro Rounded Semibold]{SF Pro Rounded}
  \setmathfont[]{STIX Two Math}
\fi
\usefonttheme{serif} % use mainfont rather than sansfont for slide text
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={444 Lecture 11.1 - O'Connor Chapter 6},
  pdfauthor={Brian Weatherson},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\let\Tiny=\tiny

 \setbeamertemplate{navigation symbols}{} 

% \usetheme{Madrid}
 \usetheme[numbering=none, progressbar=foot]{metropolis}
 \usecolortheme{wolverine}
 \usepackage{color}
 \usepackage{MnSymbol}
% \usepackage{movie15}

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
\DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\AtBeginSection[]
{
\begin{frame}
	\Huge{\color{darkblue} \insertsection}
\end{frame}
}

\renewenvironment*{quote}	
	{\list{}{\rightmargin   \leftmargin} \item } 	
	{\endlist }

\definecolor{darkgreen}{rgb}{0,0.7,0}
\definecolor{darkblue}{rgb}{0,0,0.8}

\usepackage[italic]{mathastext}
\usepackage{nicefrac}
\usepackage{istgame}

\setbeamertemplate{caption}{\raggedright\insertcaption}

%\def\toprule{}
%\def\bottomrule{}
%\def\midrule{}
\usepackage{etoolbox}
\AfterEndEnvironment{description}{\vspace{9pt}}
\AfterEndEnvironment{oltableau}{\vspace{9pt}}
\BeforeBeginEnvironment{oltableau}{\vspace{9pt}}
\AfterEndEnvironment{center}{\vspace{9pt}}
\BeforeBeginEnvironment{tabular}{\vspace{9pt}}
\AfterEndEnvironment{longtable}{\vspace{-6pt}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable} 
\usepackage{threeparttablex} 
\usepackage[normalem]{ulem} 
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{ulem}

\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0.08ex}

\aboverulesep=0ex
\belowrulesep=0ex
\renewcommand{\arraystretch}{1.2}
\AtBeginSection[]
{
    \begin{frame}
        \frametitle{Day Plan}
        \tableofcontents[currentsection]
    \end{frame}
}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{444 Lecture 11.1 - O'Connor Chapter 6}
\author{Brian Weatherson}
\date{}

\begin{document}
\frame{\titlepage}

\begin{frame}{Day Plan}
\protect\hypertarget{day-plan}{}
\tableofcontents
\end{frame}

\hypertarget{variable-learning-rate}{%
\section{Variable Learning Rate}\label{variable-learning-rate}}

\begin{frame}{Benefits to Learning}
\protect\hypertarget{benefits-to-learning}{}
\begin{itemize}
\tightlist
\item
  In normal situations, there is a benefit to learning more about your
  environment.
\item
  Indeed, there is a famous proof of this, that makes reasonably weak
  assumptions.
\item
  But in certain game theoretic contexts, the proof fails.
\item
  It is possible to benefit from being slow to learn.
\end{itemize}
\end{frame}

\begin{frame}{Chicken}
\protect\hypertarget{chicken}{}
Imagine a real-life version of Chicken with each player playing the
following strategy

\begin{itemize}
\tightlist
\item
  Stay straight unless you know that the other player will be staying
  straight. \pause
\end{itemize}

In this case, the slower learner will win.
\end{frame}

\begin{frame}{Red King Effect}
\protect\hypertarget{red-king-effect}{}
\begin{itemize}
\tightlist
\item
  This is what O'Connor is calling the Red King effect.
\item
  I mean this fairly literally; the games she is using in these models
  are I think versions of Chicken.
\item
  And the reason fast learners do badly is that they learn that the
  other party is doing something that will be disasterous if they both
  do it.
\end{itemize}
\end{frame}

\begin{frame}{Significance of This}
\protect\hypertarget{significance-of-this}{}
It's really hard to see how this can be a big part of the story of
gender inequality.

\begin{enumerate}[<+->]
\tightlist
\item
  The magnitudes are small.
\item
  The circumstances in which it arises are fairly specific, and gender
  inequality is everywhere.
\end{enumerate}
\end{frame}

\begin{frame}{Small Populations}
\protect\hypertarget{small-populations}{}
The key insight, which seems right, is that small groups learn about big
groups more rapidly than big groups learn about small groups.

\begin{itemize}
\tightlist
\item
  Australian immigrants in America can tell you a lot more about
  American social practices than native-born Americans can tell you
  about Australian immigrants.
\item
  And something similar I suspect is true about American immigrants in
  Australia.
\item
  And maybe, maybe, the result of that learning means that the small
  group will head to the nearest equilibrium, even if it is one that is
  bad for them.
\end{itemize}
\end{frame}

\hypertarget{strategies}{%
\section{Strategies}\label{strategies}}

\begin{frame}{Clarification}
\protect\hypertarget{clarification}{}
I actually didn't quite understand the game on page 141.

\begin{itemize}
\tightlist
\item
  I think it's like the bargaining game from chapter 5 except one meets
  people from both types.
\item
  And hence one's strategy can (I think) be sensitive to the type of
  player on the other side.
\item
  Presumably we see strategies in which one does something other than
  50/50 in intra-type play die out, though I'm not really sure.
\end{itemize}
\end{frame}

\begin{frame}{Lab Experiment}
\protect\hypertarget{lab-experiment}{}
But then I really couldn't understand the experiment on page 142.

\begin{itemize}
\tightlist
\item
  If you only interact with out-group members, there shouldn't be an
  effect of group size.
\item
  What matters is that these out-group interactions are common for one
  group and rare for another.
\end{itemize}
\end{frame}

\hypertarget{memory-length}{%
\section{Memory Length}\label{memory-length}}

\begin{frame}{A Quote}
\protect\hypertarget{a-quote}{}
\begin{quote}
In all three cases, the fact that one side sees more makes them less
reactive, and less likely to change strategies quickly. As Hwang et
al.~(2014) put it, ``a larger scope of vision among the well off reduces
their responsiveness to the idiosyncratic play of the poor''
\end{quote}
\end{frame}

\begin{frame}{Puzzle}
\protect\hypertarget{puzzle}{}
\begin{itemize}
\tightlist
\item
  I don't really get this.
\item
  I see how it works mathematically; if you're just reacting to what
  happened in the very last round, then you'll bounce around all over
  the place.
\item
  But who is that a decent model of?
\end{itemize}
\end{frame}

\begin{frame}{Alternative Real-World Case}
\protect\hypertarget{alternative-real-world-case}{}
\begin{itemize}
\tightlist
\item
  Everyone remembers their last X interactions.
\item
  When dealing with group g, they take the interactions with g of those
  last X and take them to be typical. \pause
\item
  But now the small group will be the one who has less random moving
  from one node to another.
\item
  I feel that this is one of those mathematical models you could just as
  easily have used to `explain' why group differences fade over time as
  why they stay.
\end{itemize}
\end{frame}

\hypertarget{utility-scales-are-arbitrary}{%
\section{Utility Scales are
Arbitrary}\label{utility-scales-are-arbitrary}}

\begin{frame}{Page 155}
\protect\hypertarget{page-155}{}
Look at the table in figure 6.14.

\begin{itemize}
\tightlist
\item
  In classical game theory, that is a perfectly symmetric game.
\item
  That's because utility scales are only defined up to positive affine
  transformation.
\item
  And so here the parties get the same return (up to transformation) as
  each other.
\end{itemize}
\end{frame}

\begin{frame}{Classical vs Evolutionary Game Theory}
\protect\hypertarget{classical-vs-evolutionary-game-theory}{}
Here I think it's really important that we're using evolutionary models.

\begin{itemize}
\tightlist
\item
  Evolutionary payout functions do not have the same invariance profiles
  as classical payout functions.
\item
  It really matters that one party gets an extra bonus.
\item
  And sure, I guess that makes sense.
\item
  But it's worth noting how far we've left anything like classical game
  theory.
\end{itemize}
\end{frame}

\begin{frame}{Big Picture}
\protect\hypertarget{big-picture}{}
\begin{itemize}[<+->]
\tightlist
\item
  Sometimes it seems that O'Connor is not making the hyper-rationality
  assumptions characteristic of classical game theory. That's a very
  good thing.
\item
  But sometimes it seems that she is making some strong irrationality
  assumptions. And that's less obviously good.
\end{itemize}
\end{frame}

\end{document}
