% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[BoldFont = SF Pro Rounded Semibold]{SF Pro Rounded}
  \setmathfont[]{STIX Two Math}
\fi
\usefonttheme{serif} % use mainfont rather than sansfont for slide text
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={444 Lecture 13.1 - Lackey Group Knowledge},
  pdfauthor={Brian Weatherson},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\let\Tiny=\tiny

 \setbeamertemplate{navigation symbols}{} 

% \usetheme{Madrid}
 \usetheme[numbering=none, progressbar=foot]{metropolis}
 \usecolortheme{wolverine}
 \usepackage{color}
 \usepackage{MnSymbol}
% \usepackage{movie15}

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
\DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\AtBeginSection[]
{
\begin{frame}
	\Huge{\color{darkblue} \insertsection}
\end{frame}
}

\renewenvironment*{quote}	
	{\list{}{\rightmargin   \leftmargin} \item } 	
	{\endlist }

\definecolor{darkgreen}{rgb}{0,0.7,0}
\definecolor{darkblue}{rgb}{0,0,0.8}

\usepackage[italic]{mathastext}
\usepackage{nicefrac}
\usepackage{istgame}

\setbeamertemplate{caption}{\raggedright\insertcaption}

%\def\toprule{}
%\def\bottomrule{}
%\def\midrule{}
\usepackage{etoolbox}
\AfterEndEnvironment{description}{\vspace{9pt}}
\AfterEndEnvironment{oltableau}{\vspace{9pt}}
\BeforeBeginEnvironment{oltableau}{\vspace{9pt}}
\AfterEndEnvironment{center}{\vspace{9pt}}
\BeforeBeginEnvironment{tabular}{\vspace{9pt}}
\AfterEndEnvironment{longtable}{\vspace{-6pt}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable} 
\usepackage{threeparttablex} 
\usepackage[normalem]{ulem} 
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{ulem}

\setlength\heavyrulewidth{0ex}
\setlength\lightrulewidth{0.08ex}

\aboverulesep=0ex
\belowrulesep=0ex
\renewcommand{\arraystretch}{1.2}
\AtBeginSection[]
{
    \begin{frame}
        \frametitle{Day Plan}
        \tableofcontents[currentsection]
    \end{frame}
}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{444 Lecture 13.1 - Lackey Group Knowledge}
\author{Brian Weatherson}
\date{}

\begin{document}
\frame{\titlepage}

\begin{frame}{Plan}
\protect\hypertarget{plan}{}
\begin{itemize}
\tightlist
\item
  For today I mostly want to discuss the five examples that I posted on
  Canvas.
\item
  So this is just a very short lecture on an argument by Jennifer
  Lackey.
\end{itemize}
\end{frame}

\begin{frame}{Emergent Group Knowledge}
\protect\hypertarget{emergent-group-knowledge}{}
Can a group know that \(A\) without any member of the group knowing that
\(A\)? \pause

\begin{itemize}
\tightlist
\item
  How does the structure of the group relate to whether this is
  possible?
\end{itemize}
\end{frame}

\begin{frame}{Case One: Compound Knowledge}
\protect\hypertarget{case-one-compound-knowledge}{}
\begin{itemize}
\tightlist
\item
  The expert on \(p\) knows that \(p\).
\item
  The expert on \(q\) knows that \(q\).
\item
  No one has asked whether \(p \wedge q\) is true.
\item
  But maybe the group knows it.
\end{itemize}
\end{frame}

\begin{frame}{Structure}
\protect\hypertarget{structure}{}
\begin{itemize}
\tightlist
\item
  This maybe feels like it will only work for structured groups.
\item
  In an unstructured group, it won't be so clear that there is an expert
  on the relevant topics.
\end{itemize}
\end{frame}

\begin{frame}{Case Two: Stored Knowledge}
\protect\hypertarget{case-two-stored-knowledge}{}
\begin{itemize}
\tightlist
\item
  The expert on \(p\) learns that \(p\).
\item
  This information is stored in the right kind of way.
\item
  Then the expert loses that knowledge. (Perhaps by dying.)
\item
  Does the group retain the knowledge that p?
\end{itemize}
\end{frame}

\begin{frame}{Structure}
\protect\hypertarget{structure-1}{}
\begin{itemize}
\tightlist
\item
  This one feels like structure shouldn't matter.
\item
  An unstructured groups can have storage mechanisms.
\end{itemize}
\end{frame}

\begin{frame}{Lackey's Argument}
\protect\hypertarget{lackeys-argument}{}
\begin{enumerate}
\tightlist
\item
  If someone, or some group, knows that \(A\), then that group can
  rationally take it for granted that \(A\) in choosing an action.
\item
  If no one in the group knows that \(A\), the group cannot take the
  allegedly known things for granted in rationally choosing an action.
\item
  So in at least example five, and maybe others, the groups do not have
  knowledge.
\end{enumerate}
\end{frame}

\begin{frame}{Knowledge and Action}
\protect\hypertarget{knowledge-and-action}{}
\begin{itemize}
\tightlist
\item
  Lackey's premise 1 is a version of an important principle connecting
  knowledge and action.
\item
  The premise is really super controversial.
\item
  Lots of people think that you cannot always take for granted things
  that you know.
\item
  For example, they think that you can simultaneously know that you
  turned the oven off, and not be able to take this for granted when
  deciding to check whether the oven is off.
\item
  But I think this principle is pretty plausible.
\end{itemize}
\end{frame}

\begin{frame}{Knowledge and Action}
\protect\hypertarget{knowledge-and-action-1}{}
\begin{itemize}
\tightlist
\item
  But premise 2 seems more dubious to me.
\item
  Imagine that in the past I was told that in 1896 the mayor of Ann
  Arbor was Warren Walker.
\item
  And now I can't quite recall his name.
\item
  I can't simply take that fact for granted in action.
\item
  But maybe I did know it all along.
\end{itemize}
\end{frame}

\begin{frame}{Knowledge and Action}
\protect\hypertarget{knowledge-and-action-2}{}
\begin{itemize}
\tightlist
\item
  Being able to take something for granted arguably requires not just
  knowledge, but access, and that's a stronger condition.
\item
  And it's true that the group in Bird's case doesn't have access to the
  knowledge.
\end{itemize}
\end{frame}

\begin{frame}{Emergence}
\protect\hypertarget{emergence}{}
\begin{itemize}
\tightlist
\item
  Note that the possibility of group knowledge without individual
  knowledge doesn't entail that there is anything like a group mind
  above and beyond the individual mind.
\item
  These cases are still compatible with thorough going reductionism.
\item
  It's just that we can't reduce group knowledge to individual
  knowledge. \pause
\item
  The same pattern occurs in a lot of other topics.
\item
  You can often have reduction without reduction on this very question.
\end{itemize}
\end{frame}

\end{document}
