---
title: "444 Lecture 2.4 - Dominance"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

- Explain strong dominance and weak dominance.

## Associated Reading

Bonanno, section 2.2.

## A Simple Game

```{r}
game <- tribble(
  ~Moves,     ~Left,     ~Right,
  "Up",      "4, 1", "2, 0",
  "Down",    "3, 0", "1, 1"
)
gameformat(game)
```

Here's how to read this table.

> 1. Two players, call them Row and Column.
> 2. Row chooses the row, Column chooses the column - between them they choose a cell.
> 3. Each cell has two numbers - the first is Row's payout, the second is Column's payout.

## Strong Dominance

```{r}
game <- tribble(
  ~Moves,     ~Left,     ~Right,
  "Up",      "4, 1", "2, 0",
  "Down",    "3, 0", "1, 1"
)
gameformat(game)
```

- Whatever Column does, Row is better off playing Up rather than Down.
- We say that Up **strongly dominates** Down.

## Strong Dominance

```{r}
game <- tribble(
  ~Moves,     ~Left,     ~Right,
  "Up",      "4, 1", "2, 0",
  "Middle",  "5, 0", "0, 0",
  "Down",    "3, 0", "1, 1"
)
gameformat(game)
```

- Adding options doesn't change things.
- Up still dominates Down, even if it isn't always best.

## Strong Dominance

```{r}
game <- tribble(
  ~Moves,     ~Left,     ~Right,
  "Up",      "3, 1", "0, 0",
  "Middle",  "2, 0", "2, 0",
  "Down",    "0, 0", "3, 1"
)
gameformat(game)
```

- This is **not** a case of dominance.
- Even though Middle is never the highest value, it isn't dominated by any one option.

## Strong Dominance

Strategy $S_1$ strongly dominates strategy $S_2$ if for any strategy $S$ by the other player(s), if $S$ is played, then $S_1$ returns a higher payoff than $S_2$.

## Weak Dominance

Strategy $S_1$ weakly dominates strategy $S_2$ if for any strategy $S$ by the other player(s), if $S$ is played, then $S_1$ returns a payoff that is at least as high $S_2$, and for some strategy by the other player(s), $S_1$ returns a higher payoff than $S_2$.

- The difference is that weak dominance allows for **ties**.

## Two Dominance Notions

Strong Dominance

- Always better.

Weak Dominance

- Never worse.
- Sometimes better.

## Weak Dominance

```{r}
game <- tribble(
  ~Moves,     ~Left,     ~Right,
  "Up",      "4, 1", "2, 0",
  "Down",    "3, 0", "\\textbf{2}, 1"
)
gameformat(game)
```

- I've changed the payoffs in the bottom right cell.
- Now Up does not strongly dominate Down.
- But it does weakly dominate Down.

## For Next Time

We'll look at some examples of famous two by two by two games.