---
title: "444 Lecture 2.6 - Iterated Deletion"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

To describe the strategy of solving games by iteratively deleting strategies.

## Reading

Bonanno, section 2.5

## Initial Idea

> - If an option is strongly dominated, it shouldn't be chosen.
> - In the simple case, if all options but one are strongly dominated, that one should be chosen.
> - But we can say more than this.
> - If a strategy only makes sense if the other player plays a dominated strategy, then it doesn't make sense.
> - Let's work through some examples to see how this works in practice.

## Easy Example

```{r}
game <- tribble(
  ~Moves,  ~Left, ~Right,
  "Up",   "4, 1", "2, 2",
  "Down", "3, 3", "1, 4"
)
gameformat(game)
```

We can solve this using just domination.

> - Up dominates Down, so Row should play Up.
> - Right dominates Left, so Column should play Right.
> - So the solution is Up/Right.

## Only Slightly Harder Example

```{r}
game <- tribble(
  ~Moves,  ~Left, ~Right,
  "Up",   "4, 0", "2, 1",
  "Down", "3, 1", "1, 0"
)
gameformat(game)
```

Now Column doesn't have a dominating option, but that doesn't stop us.

> - Up dominates Down, so Row should play Up.
> - If Row is playing Up, Right is better than Left (1 beats 0).
> - So since Row is playing Up, Column should play Right.
> - So the solution (again) is Up/Right.

## Iterated Dominance

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "4, 2",  "3, 1", "0, 0",
  "Middle", "3, 0",  "2, 2", "1, 1",
  "Down",   "2, 0",  "1, 0", "0, 3"
)
gameformat(game)
```

We can't immediately solve this with dominance, but we can in a few steps.

## Iterated Dominance

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "4, 2",  "3, 1", "0, 0",
  "Middle", "3, 0",  "2, 2", "1, 1",
  "Down",   "2, 0",  "1, 0", "0, 3"
)
gameformat(game)
```

- Note first that Middle dominates Down.
- So Down should not be played.
- In fact, we might even act as if it is not there.

## Iterated Dominance

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center, ~Right,
  "Up",     "4, 2",  "3, 1", "0, 0",
  "Middle", "3, 0",  "2, 2", "1, 1"
)
gameformat(game)
```

- Here's what happens if we **delete** the dominated option Down.
- Now Center dominates Right.
- It didn't a minute ago - Right is a better response to Down than Center is - but Down is deleted.
- So Right is out, and we'll delete it too.

## Iterated Dominance

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center,
  "Up",     "4, 2",  "3, 1",
  "Middle", "3, 0",  "2, 2"
)
gameformat(game)
```

- In this game, Up dominates Middle.
- So Middle has to go.

## Iterated Dominance

```{r}
game <- tribble(
  ~Moves,    ~Left, ~Center,
  "Up",     "4, 2",  "3, 1"
)
gameformat(game)
```

- And in this game, Left dominates Center.
- So the solution to the game is Up/Left.

## General Strategy

- Start deleting dominated strategies.
- Then see if some strategies are dominated in the new version of the game.
- If you're lucky, the result will be that just one option for each player is left.
- If so, we'll call that the solution of the game.

## For Next Time

- We'll see some complications that arise when we delete weakly dominated strategies.