---
title: "444 Lecture 5.4 - Finding Mixed Strategy Equilibria"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

Discuss how we can find mixed strategy equilibria.

## Reading

Bonanno, Section 6.3.

## Basic Idea

- In equilibria, the other player is willing to play a mixed strategy.
- That requires that they be indifferent between other strategies.
- So we find the equilibria by finding the mixture that makes them indifferent.

## Example

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "5, 2", "1, 3", 
  "Down",  "2, 2", "3, 0"
)
gameformat(game)
```

- You can see fairly quicklythat there is no pure strategy equilibria.
- So the equilibria must be a mixed strategy equilibria.

## Theory

What does it take for Column to play a mixed strategy in equilibria?

- Assume that Left has a higher expected return than Right.
- The expected return of a mixed strategy is a weighted average of the expected returns of Left and Right.
- If Left has a higher expected return than Right, that weighted average will be strictly between the expected returns of Left and Right.
- And that means it can't be an equilibrium, since in equilibrium there is no alternative with a higher expected return. \pause
- And the same reasoning shows Right can't have a higher expected return than Left.

## Theory

So we are trying to find the mixture such that Column is indifferent between Left and Right.

- The other crucial thing to remember is that probabilities add to 1.
- So when working out Row's strategy, there is only one variable.
- Once we set the probability of Row playing Up to $x$, that sets all the probabilities, because the probablity of playing Down is $1-x$.

## A Note

I'm only going to go over cases where the mixed strategy equilibrium involves a mixture of two pure strategies.

- There are cases where the mixed strategy equilibrium involves mixtures of 3 or more pure strategies.
- Rock, Paper, Scissors is the simplest such example.
- But in general the math of calculating these is considerably fancier than what we'll be doing, and I'll stick to cases where the mixed strategy equilibrium only involves 2 pure strategies.

## Back to the Example

```{r}
gameformat(game)
```

- Assume Row plays Up with probability $x$, and Down with probability $1-x$.
- Our job is to find an $x$ such that the expected return of Left and Right is the same.

## Left and Right

```{r}
gameformat(game)
```

- The expected return of Left is $2x + 2(1-x)$, i.e., $2$.
- The expected return of Right is $3x + 0(1-x)$, i.e., $3x$.

## Row's Strategy.

```{r}
gameformat(game)
```

- So $2 = 3x$, so $x = \nicefrac{2}{3}$.
- So Row's strategy is to play Up with probability $\nicefrac{2}{3}$, and hence Down with probability $\nicefrac{1}{3}$.

## 
- The expected return of Right is $3x + 0(1-x)$, i.e., $3x$.

## Onto Column

```{r}
gameformat(game)
```

- Assume Column plays Left with probability $x$, and Right with probability $1-x$.
- Our job is to find an $x$ such that the expected return of Up and Down is the same.

## Left and Right

```{r}
gameformat(game)
```

- The expected return of Up is $5x + 1(1-x)$, i.e., $4x + 1$.
- The expected return of Down is $2x + 3(1-x)$, i.e., $3 - x$.

## Column's Strategy.

\begin{align*}
4x + 1 &= 3 - x \\
5x + 1 &= 3 \\
5x    &= 2 \\
x    &= \nicefrac{2}{5}
\end{align*}

So Column's strategy is to play Left with probability $\nicefrac{2}{5}$, and hence Right with probability $\nicefrac{3}{5}$.

## Takeaways

- To find a player's move probabilities in equilibria, look to the other player's payouts.
- Try to make the other player indifferent between their choices.

## Extra Steps

- I'm not going to go over more complicated examples on the slides, but there is an extra step you can do (and which we can discuss in class if you're interested).
- Sometimes you can find the mixed strategy equilibria of a game with more than 2 moves by first deleting **strongly** dominated strategies.
- Bonanno works through an example like this.
- I'm going to come back to it later, but for now I'll just stick to this example.

## For Next Time

I'm going to start on an idea I want to work through very slowly, and spend a bit of time on - the idea that a mixture of strategies can dominate another strategy.