---
title: "444 Lecture 5.5 - Dominance by Mixture"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

Discuss a new form of dominance reasoning - mixed strategy dominance.

## Reading

Bonanno, Section 6.4.

## Basic Example

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 0", 
  "Middle", "1, 0", "1, 0",
  "Down",  "0, 0", "3, 0"
)
gameformat(game)
```

This is a bit boring for Column, but let's focus on Row for now.

## Dominance Reasoning

```{r}
gameformat(game)
```

At first it looks like there are no dominated strategies.

- Up does worse than Middle and Down if Column plays Right, so it doesn't dominate anything.
- Middle does worse that Up if Column plays Left, and worse than Down if Column plays Right.
- Down does worse than both of them if Column plays Left.

## Dominance Reasoning

```{r}
gameformat(game)
```

But compare these two strategies.

- Middle
- The mixed strategy of Up with probability 0.5, and Down with probability 0.5.

## Dominance Reasoning

```{r}
gameformat(game)
```

- Middle gets an actual return of 1 whatever Column does.
- The mixed strategy gets an expected return of 1.5 whatever Column does.
- So it has a higher expected return given Left (1.5 > 1), and a higher expected return given Right (1.5 > 1).

## Dominance Reasoning

```{r}
gameformat(game)
```

- If that happens, then we'll say that Middle is dominated by this mixture.
- When we're deleting dominated strategies, we should delete it too.

## Nash and Dominance

- A strategy that is dominated by a mixture like this can never be part of a Nash equilibrium.
- After all, the player would be better off playing the mixture than playing it, so it fails the test that there is nothing better to do.
- So being able to find these dominating mixtures can be very helpful in working out what the Nash equilibrium is.

## Rational Play and Dominance

- But even beyond that, it seems wrong to play strategies that are dominated in this way.
- If you're thinking about playing Middle (as Row), you increase your expected return by simply flipping a coin to choose between Left and Right.
- So that's what you should do.

## For Next Time

We'll connect this expanded notion of dominance up to an expanded notion of best responses.