---
title: "444 Lecture 5.6 - Best Responses"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

Discuss how to think about best responses work once mixed strategies are on the table.

## Reading

Bonanno, Section 6.4.

## An example

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 0", 
  "Middle", "2, 0", "2, 0",
  "Down",  "0, 0", "3, 0"
)
gameformat(game)
```

-   Up is the best response to Left.
-   Down is the best response to Right.
-   Is Middle the best response to anything?

## Best Responses

```{r}
gameformat(game)
```

Yes!

-   Middle is the best response to the mixed strategy Left with probability 0.5, Right with probability 0.5.
-   It gets 2, the other options have an expected return of 1.5.

## Varieties of Mixed Strategies

```{r}
gameformat(game)
```

-   Middle is the best thing to do if you know Column is going to flip a coin to decide what to do. \pause
-   But it's also the best thing to do if you have no idea what Column is going to do, and the best you can do is say it's 50/50 what they are going to do.
-   So it's actually pretty easy to think of situations where Middle is the smart play.

## Best Response

-   A strategy $S$ is a **best response** just in case...
-   There is some probability distribution over the other player's strategies and ...
-   No strategy has a higher expected return than $S$ given that probability distribution. \pause
-   Note that this allows for ties.
-   Weakly dominated strategies can even be best responses in this sense. \pause
-   This definition also covers mixed strategies; they can also be best responses.

## A Surprising Theorem

-   Say a strategy is **undominated** if no other strategy, pure or mixed, strongly dominates it. \pause
-   And it is a **best response** if it does as well as anything, given at least one probability distribution.\pause
-   Here's the surprising theorem:

> The strategies that are best responses are just the same strategies as those that are undominated.

## Best Reponses

-   This relates back to something I was saying in the last lecture.
-   The strategies that are dominated by mixtures didn't seem to make sense - you could just play the mixtures.
-   But here's another property that they have - they are never best responses.
-   And if they are not best responses, no one can play them while maximising expected utility.
-   Whatever probability you give to the other player's play, if you maximise expected utility you will play a best response.
-   And you should maximise expected utility.

## For Next Time

-   I'll introduce a new solution concept, one that say playing a best response is not just necessary for rationality, it is also sufficient.
