---
title: "444 Lecture 5.7 - Rationalizable Strategies"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

```{r, include=FALSE}
source("kableformat.R")
```

## Plan

To introduce the idea of rationalizable strategies.

## Reading

Bonanno, section 6.4

## Playing Best Responses

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 1", 
  "Middle", "1, 1", "1, 0",
  "Down",  "0, 0", "3, 1"
)
gameformat(game)
```

In this game, the best responses are:

- Row can play Up (best response to Left) or Down (best response to Right);
- Column can play Left (best response to Middle) or Right (best response to either Up or Down).

## Playing Best Responses

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 1", 
  "Middle", "1, 1", "1, 0",
  "Down",  "0, 0", "3, 1"
)
gameformat(game)
```

- But Middle is not a best response.
- It is dominated by the 50/50 mixture of Left and Right.

## Iterated Best Responses

```{r}
game <- tribble(
  ~Moves,         ~Left, ~Right,
  "Up",  "3, 0", "0, 1", 
  "Middle", "1, 1", "1, 0",
  "Down",  "0, 0", "3, 1"
)
gameformat(game)
```

- So while Left is a best response...
- It is not a best response to a best response.

## Iterated Best Responses

- That makes it seem irrational to play Middle. \pause
- I could build more complicated examples, where we had cases that are best responses to best responses, but not best responses to best responses to best responses. \pause
- Actually we've already seen such a case.
- In the Ice Cream game, 2 is a best response to 1, which is a best response to 0. 
- But 2 is not a best response to any best response to a best response.

## Iterated Best Responses

- Some strategies are at the start of an infinite chain $S_1, S_2, \dots$ where each strategy is a best response to the one that comes after it.
- Call these the **rationalizable** strategies.

## Infinite Chains

Here is one way to get an infinite chain like this.

- If the pair $\langle S_1, S_2 \rangle$ is a Nash equilibrium, ...
- Then $S_1$ is a best response to $S_2$, which is a best response to $S_1$, which is a best response to $S_2$, which ... \pause
- But you don't only need to use Nash equilibria.
- Think about Rock, Paper, Scissors.
- Rock is a best response to Scissors, which is a best response to Paper, which is a best response to Rock, which is...
- But Rock is not part of a Nash equilibrium.

## Rationalizability

I'm not going to prove this, but the following turns out to be true.

- The strategies that can be at the start of these infinite chains ...
- Are exactly those strategies that survive iterated deletion of strongly dominated strategies ...
- Provided we include dominance by mixtures when we're doing the deleting.

## Philosophical Payoff

Some economists, and a few philosophers, have argued that this is the key philosophical notion in game theory.

- They say that a strategy is rational to play if and only if it is rationalizable in this sense. \pause
- In economics, this is very much a **heterodox** view.
- Note that this view is more permissive than the view that rational players will choose Nash equilibria.
- All Nash equilibria are rationalizable, but some rationalizable strategies (e.g., Rock!), are not Nash equilibria. \pause
- Most economists think that if there is a key notion in game theory, it is **less permissive** than Nash equilibrium.

## For Next Time

- We'll close this out by going back to Nash, and asking why Nash equilibrium is philosophically significant.
