---
title: "444 Lecture 7.1 - Bayesian Equilibrium"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

## What is Rational Here?

<!-- \begin{center} -->
<!-- \begin{istgame} -->
<!-- %\setistgrowdirection'{east} -->
<!-- \xtdistance{15mm}{30mm} -->
<!-- \istroot(0){Alice} -->
<!--   \istb{A}[al]{(1,1)} -->
<!--   \istb{D}[ar] -->
<!--   \endist -->
<!-- \istroot(1)(0-2)<above right>{Alice} -->
<!--   \istb{L}[al] -->
<!--   \istb{R}[ar] -->
<!--   \endist -->
<!-- \xtdistance{10mm}{20mm} -->
<!-- \istroot(2)(1-1) -->
<!--   \istb{l}[al]{(2,2)} -->
<!--   \istb{ð“‡}[ar]{(0,0)} -->
<!--   \endist -->
<!-- \istroot(3)(1-2) -->
<!--   \istb{l}[al]{(2,2)} -->
<!--   \istb{ð“‡}[ar]{(0,0)} -->
<!--   \endist -->
<!-- \xtInfoset(2)(3){Billie} -->
<!-- \end{istgame} -->
<!-- \end{center} -->

\begin{center}
\begin{istgame}
%\setistgrowdirection'{east}
\xtdistance{15mm}{30mm}
\istroot(0){Alice}
  \istb{A}[al]{(1,1)}
  \istb{B}[r]
  \istb{C}[ar]
  \endist
\xtdistance{10mm}{20mm}
\istroot(1)(0-2)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\istroot(2)(0-3)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\xtInfoset(1)(2){Billie}
\end{istgame}
\end{center}

> - Intuitively we should end up with one of the 2,2 outcomes.
> - But how theoretically can we get that?

## Strategy Table

```{r, include=FALSE}
source("kableformat.R")
```

```{r}
game <- tribble(
  ~Moves,         ~l, ~r,
  "A",  "1, 1", "1, 1", 
  "B", "2, 2", "0, 0",
  "C",  "2, 2", "0, 0"
)
gameformat(game)
```

Note that $\langle A, r \rangle$ is a Nash equilibrium.

## Subgame Perfection

\begin{center}
\begin{istgame}
%\setistgrowdirection'{east}
\xtdistance{15mm}{30mm}
\istroot(0){Alice}
  \istb{A}[al]{(1,1)}
  \istb{B}[r]
  \istb{C}[ar]
  \endist
\xtdistance{10mm}{20mm}
\istroot(1)(0-2)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\istroot(2)(0-3)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\xtInfoset(1)(2){Billie}
\end{istgame}
\end{center}

- There are no subgames (think about why) - so $\langle A, r \rangle$ is also subgame perfect.

## Intuition

- It is absurd for Billie to play r if it gets that far.
- We need a theory that says this is absurd.
- This is just the kind of thing subgame perfect equilibrium was introduced for, but it isn't working for technical reasons about the definition of subgames.
- I'm not sure if there is a completely standard solution here, but I wanted to set out an approach that's consistent with current philosophy.

## Bayesian Equilibrium

- An equilibrium is a pair of behavioral dispositions.
- Each behavioral disposition gives a probability of each choice at each node the player may have to choose at.
- In equilibrium, each player has their own disposition from the pair, and believes (with certainty) that the other player has the other disposition from the pair.
- If there is a move made by Nature, each player has the correct probability for each of Nature's possible moves.
- At every stage, each Player maximises expected utility given their beliefs about the other.

## Re-formulation

This is more or less equivalent.

- Each player starts with a probability distribution over outcomes of the game.
- In equilibrium, these are the same, and the players have correct probabilities about the moves nature will make.
- When something happens (a move is revealed), the players update by conditionalisation if the event has positive probability.
- When something unexpected (probability zero) happens, the players just pick a new probability.
- In equilibrium, both players know how both players are disposed to react in each of these cases.
- Everyone is always maximising expected utility.

## Back to the Game

\begin{center}
\begin{istgame}
%\setistgrowdirection'{east}
\xtdistance{15mm}{30mm}
\istroot(0){Alice}
  \istb{A}[al]{(1,1)}
  \istb{B}[r]
  \istb{C}[ar]
  \endist
\xtdistance{10mm}{20mm}
\istroot(1)(0-2)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\istroot(2)(0-3)
  \istb{l}[al]{(2,2)}
  \istb{r}[ar]{(0,0)}
  \endist
\xtInfoset(1)(2){Billie}
\end{istgame}
\end{center}

> - At the B/C information set, Billie must have some probability between B and C.
> - Whatever it is, l has higher expected utility that r.
> - Alice knows this, so will choose B or C rather than A.

## For Next Time

- I'll look at two puzzle cases.
- If you're pressed for time, skip ahead to the following lecture.