---
title: "444 Lecture 7.2 - Two Puzzles about Bayesian Equilibrium"
author: "Brian Weatherson"
mainfont: SF Pro Rounded
output:
  beamer_presentation:
    md_extensions: +link_attributes+fenced_divs
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: 
        - 444-beamer-header.tex
        - extra-space.tex
        - kableextra-dependencies.tex
mathfont: STIX Two Math
mainfontoptions: BoldFont = SF Pro Rounded Semibold
---

## First Puzzle

\begin{center}
\begin{istgame}
%\setistgrowdirection'{east}
\xtdistance{15mm}{30mm}
\istroot(0){Alice}
  \istb{A}[al]{(2,2)}
  \istb{B}[r]
  \istb{C}[ar]
  \endist
\xtdistance{10mm}{20mm}
\istroot(1)(0-2)
  \istb{l}[al]{(4,4)}
  \istb{r}[ar]{(1,0)}
  \endist
\istroot(2)(0-3)
  \istb{l}[al]{(3,0)}
  \istb{r}[ar]{(0,4)}
  \endist
\xtInfoset(1)(2){Billie}
\end{istgame}
\end{center}

- I don't really know what to do here.

## Strategy Table

```{r, include=FALSE}
source("kableformat.R")
```

```{r}
game <- tribble(
  ~Moves,         ~l, ~r,
  "A",  "2, 2", "2, 2", 
  "B", "4, 4", "1, 0",
  "C",  "3, 0", "0, 4"
)
gameformat(game)
```

Note that $\langle A, r \rangle$ is a Nash equilibrium, and B dominates C.

## Bayesian Equilibrium

The following is even a Bayesian Equilibrium

- Alice plays A.
- Billie believes with probability 1 that Alice will play A.
- If Billie finds herself at the B/C set, she will believe that Alice played C.
- So she will do what's best for her given this belief, i.e., play r.
- Alice knows this.

Alice plays A and gets 2, and she believes she would get 1 if she played B and 0 if she played C. So she's doing the thing that's best by her lights.

## Wait a Minute!

- Billie is disposed to believe that if Alice does something weird (play B or C), she will do something really weird (play a dominated strategy).
- Is this an OK thing for Billie to believe?
- It seems a bit weird.
- Maybe if Alice has not given Billie conclusive evidence that she will do something bizarre - i.e., play a dominated strategy - it's wrong to believe that she's done something bizarre.
- So if we get to B/C, Billie should believe we're at B, so should play l, and knowing that, Alice should play B.

## Which is right?

- I don't really know.
- Here we're already into contested territory.
- Let's take one further step into contested territory.

## Second Puzzle

\begin{center}
\begin{istgame}
%\setistgrowdirection'{east}
\xtdistance{15mm}{30mm}
\istroot(0){Alice}
  \istb{A}[al]{(3,3)}
  \istb{B}[r]
  \istb{C}[ar]
  \endist
\xtdistance{10mm}{20mm}
\istroot(1)(0-2)
  \istb{l}[al]{(4,4)}
  \istb{r}[ar]{(0,0)}
  \endist
\istroot(2)(0-3)
  \istb{l}[al]{(2,0)}
  \istb{r}[ar]{(1,4)}
  \endist
\xtInfoset(1)(2){Billie}
\end{istgame}
\end{center}

- I really don't know what to do here.

## Why is it Puzzling

- $\langle A, r \rangle$ is a Bayesian (and Nash and subgame perfect) equilibrium.
- But maybe Alice should choose B. \pause
- Note that A dominates C.
- So if Billie knows that Alice doesn't choose dominated options, and this survives learning that Alice has chosen B or C, then Billie will know that Alice has chosen B.
- And then Billie will choose l, so Alice should choose B.

## Two Big Questions

1. Are there philosophical grounds to change our theory of equilibrium selection to make Alice choose B in both of these games?
2. If we want to do that, what's the best mathematical theory that generates the intended result?

- Both of these are hard questions, but not one's I'm going to address in this course. 
- We have to stop somewhere, and there are always more questions like this to ask and answer. 
- Instead I'm going to a special class of games: signaling games.